---
title: "Live Session Unit 3 Assignment"
author: "David Nguyen"
date: "September 18, 2018"
output: html_document
---

#1. GitHub Cloning

Code used to clone the GitHub repository to my local machine using Git Bash:

David@DESKTOP-97U2R5B MINGW64 ~  
$ pwd #print working directory  
/c/Users/David

David@DESKTOP-97U2R5B MINGW64 ~  
$ cd /c/Users/David/Documents/GitHub #create new directory

David@DESKTOP-97U2R5B MINGW64 ~/Documents/GitHub  
$ git clone https://github.com/awesomedata/awesome-public-datasets.git #clone the repository to the new directory  
Cloning into 'awesome-public-datasets'...  
remote: Counting objects: 1484, done.  
remote: Total 1484 (delta 0), reused 0 (delta 0), pack-reused 1484  
Receiving objects: 100% (1484/1484), 565.76 KiB | 349.00 KiB/s, done.  
Resolving deltas: 100% (866/866), done.

#2. Data Summary

```{r, echo=TRUE}
#a. Code to read and assign the Titanic data:

df <- read.csv(file="titanic.csv", header=TRUE, sep=",") #read and assign the Titanic data in R

#b. Output and bar graph for the number of females and males aboard the Titanic:

table(df$Sex) #number of males and females

barplot(table(df$Sex), xlab="Gender", ylab="Number of People", main="Number of Females and Males on the Titanic") #bar graph for the number of females and males on the titanic

#c. Output of the means of age, fare, and survival:

apply(df[,c("Age", "Fare", "Survived")], 2, mean, na.rm=TRUE) #mean of age, fare, and survived
```

#3. Function Building

```{r, echo=TRUE}
#a. Objects for the median age, the minimum and maximum Duration of sleep, and the mean and standard deviation of the Rosenberg Self Esteem scale (RSES):

sleepfunction <- function(x) {
  sleep <- read.csv(file="sleep_data_01.csv", header=TRUE, sep=",") #read and assign the Sleep data in R
  medianage <- median(sleep[,"Age"], na.rm=TRUE) #median age of sleep data
  minduration <- min(sleep[,"Duration"], na.rm=TRUE) #min duration of sleep
  maxduration <- max(sleep[,"Duration"], na.rm=TRUE) #max duration of sleep
  meanrses <- mean(sleep[,"RSES"], na.rm=TRUE) #mean of the RSES
  sdrses <- sd(sleep[,"RSES"], na.rm=TRUE) #standard deviation of the RSES
  
#b. Data frame object consisting of the median age, the RSES mean and standard deviation respectively divided by five, and the range of duration:

  meanrses5 <- meanrses/5 #mean of rses divided by 5
  sdrses5 <- sdrses/5 #standard deviation of rses divided by 5
  rangeduration2numbers <- range(sleep[,"Duration"], na.rm=TRUE) #range duration of sleep
  rangeduration <- rangeduration2numbers[2] - rangeduration2numbers[1] #range duration of sleep as one number
  report <- data.frame(medianage, meanrses5, sdrses5, rangeduration) #data frame with the previous objects
  
#c. Change column names:
  
  colnames(report) <- c("MedianAge", "SelfEsteem", "SE_SD", "DurationRange") #new column names
  report #variable of the report
  
#d. Rounding of the report:
  
  finalreport <-round(report, digits = 2) #round to 2 digits
  finalreport #variable of the final report
  print(finalreport) #print final report
  }

#e. Run the function:

sleepfunction(sleep)
```

#4. FiveThirtyEight Data

```{r, echo=TRUE}
#a. Install the fivethirtyeight package:

#I did this in the console using:
#install.packages("fivethirtyeight")

#b. Assign the 22nd data set:

library(fivethirtyeight)

fivethirtyeightpackage <- data(package = "fivethirtyeight")

df <- as.data.frame(get(fivethirtyeightpackage$results[22,"Item"]))

#can aslo be done with:
#df <- fivethirtyeight::college_recent_grads

#c. The URL link is:

vignette("fivethirtyeight", package = "fivethirtyeight") #more detailed list of the data sets

#http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/

#d. The Dimensions and column names:

dim(df) #dimensions of college_recent_grads

colnames(df) #column names of college_recent_grads
```

#5. Data Summary:

```{r, echo=TRUE}
#a. Column names and number of columns:

colnames(df) #column names

length(colnames(df)) #number of columns

#b. Count of each unique major category:

major_count <- table(df$major_category) #count of each major category

#c. Plot of major count:

par(las=2) #makes text perpendicular to the axis
barplot( major_count, horiz = TRUE, main = "Number of Students per Major", xlab = "Number of Students",ylab="Major", col=c("Red") ) #barplot of major count

#d. Write the fivethirtyeight data to a csv file:

write.table( major_count, file = "fivethirtyeight.csv", row.names = FALSE, sep=",", col.names = c("major_category", "freq")) #writes data as csc file
```

#6.The Codebook:
a. New Repo on GitHub:

I started a new repository on GitHub.

b. README.md file:

I created a README.md file which details my repo.

c. Nested directories:

I created nested directories.

d. Link to this GitHub:

Here is the link to this GitHub:

https://github.com/daveknockwin/SMU-MSDS