---
title: "Live Session Unit 4 Assignment"
author: "David Nguyen"
date: "September 25, 2018"
output: html_document
---

#1. Harry Potter Cast

a. In the IMDB, there are listings of full cast members for movies. Navigate to http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1. Feel free to View Source to get a good idea of what the page looks like in code.

b. Scrape the page with any R package that makes things easy for you. Of particular interest is the table of the cast in order of crediting. Please scrape this table (you might have to fish it out of several of the tables from the page) and make it a data.frame() of the cast in your R environment.

```{r, echo=TRUE}
library(XML)
library(rvest)
#To scrape the page:
url <- "http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1"
readurl <- read_html(url)
readurl
readurl %>%
html_nodes(css = "table")
table_cast = (readurl %>% html_nodes(css = "table"))[[3]] %>%
html_table()
cast <- data.frame(table_cast)
head(cast)
```

c. Clean up the table.

- It should not have blank observations or rows, a row that should be column names, or just '.'

- It should have intuitive column names (ideally 2 to start - Actor and Character)

```{r, echo=TRUE}
#To clean the table:
cast_1 <- cast[-1,c(-1, -3)]
names(cast_1) <- c("Actor", "Character")
head(cast_1)
```

- In the film, Mr. Warwick plays two characters, which makes his row look a little weird. Please replace his character column with just "Griphook / Professor Filius Flitwick" to make it look better.

```{r, echo=TRUE}
#To find the line containing Mr. Warwick:
grep("Warwick", cast_1$Actor)
```

Line 10 contains Mr. Warwick.

```{r, echo=TRUE}
#To replace Mr. Warwick's character column:
print(cast_1[10,])
cast_1[10,] <- c("Warwick Davis", "Griphook / Professor Filius Flitwick")
print(cast_1[10,])
```

- One row might result in "Rest of cast listed alphabetically" - remove this observation.
	
```{r, echo=TRUE}
#To find the line with "Rest of cast listed alphabetically":
grep("Rest of cast listed alphabetically", cast_1)
#I found that these words are in both columns. To check which line in order to delete it:
grep("Rest of cast listed alphabetically", cast_1$Actor)
cast_2 <- cast_1[-92,]
#To check that these words aren't anywhere:
grep("Rest of cast listed alphabetically", cast_2$Actor)
grep("Rest of cast listed alphabetically", cast_2$Character)
```

d. Split the Actor's name into two columns: FirstName and Surname. Keep in mind that some actors/actresses have middle names as well. Please make sure that the middle names are in the FirstName column, in addition to the first name (example: given the Actor Frank Jeffrey Stevenson, the FirstName column would say "Frank Jeffrey.")

e. Present the first 10 rows of the data.frame() - It should have only FirstName, Surname, and Character columns.

```{r, echo=TRUE}
library(tidyr)
#To split the actor's names into two columns and present the first 10 rows of the data frame:
cast_3 <- extract(cast_2, Actor, c("FirstName", "Surname"), "([^ ].+) (.*)")
head(cast_3,10)
```

#2. SportsBall

a. On the ESPN website, there are statistics of each NBA player. Navigate to the San Antonio Spurs current statistics (likely http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs). You are interested in the Shooting Statistics table.

b. Scrape the page with any R package that makes things easy for you. There are a few tables on the page, so make sure you are targeting specifically the Shooting Statistics table.

```{r, echo=TRUE}
#To scrape the page:
url <- "http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs"
San_Antonio_Spurs <- read_html(url)
San_Antonio_Spurs
San_Antonio_Spurs %>%
html_nodes(css = "table")
table_Shooting = (San_Antonio_Spurs %>% html_nodes(css = "table"))[[2]] %>%
html_table()
```

c. Clean up the table (You might get some warnings if you're working with tibbles)

- You'll want to create an R data.frame() with one observation for each player. Make sure that you do not accidentally include blank rows, a row of column names, or the Totals row in the table as observations.

```{r, echo=TRUE}
#To check the head:
Shooting <- data.frame(table_Shooting)
head(Shooting)
#To rename the headers, then delete the 1st, 2nd, and last lines:
names(Shooting) <- Shooting[2,]
Shooting <- Shooting[c(-1,-2,-20),]
head(Shooting)
```

- The column PLAYER has two variables of interest in it: the player's name and their position, denoted by 1-2 letters after their name. Split the cells into two columns, one with Name and the other Position.

```{r, echo=TRUE}
#To split the cells into two columns:
Shooting_1 <- extract(Shooting, PLAYER, c("Name", "Position"), "([^ ].+) (.*)")
#To remove the "," in the 1st column:
Shooting_1$Name <- gsub('.{,}$', '', Shooting_1$Name)
head(Shooting_1)
```

- Check the data type of all columns. Convert relevant columns to numeric. Check the data type of all columns again to confirm that they have changed!

```{r, echo=TRUE}
#To check the data type of all columns, then convert relevant columns to numeric:
str(Shooting_1)
cols_to_change <- c(3:16)
for(i in cols_to_change){
     class(Shooting_1[, i]) = "numeric"
}
str(Shooting_1)
```

d. Create a colorful bar chart that shows the Field Goals Percentage Per Game for each person. It will be graded on the following criteria.

- Informative Title, centered

- Relevant x and y axis labels (not simply variables names!)

- Human-readable axes with no overlap (you might have to flip x and y to fix that). Note: You do not have to convert the decimal to a percentage.

- Color the columns by the team member's position (so, all PF's should have the same color, etc.)

```{r, echo=TRUE}
library(ggplot2)
#To create the bar chart:
mytheme <- theme(plot.title = element_text(face = "bold.italic",size= 14, color = "black"), axis.text.x = element_text(size = 9, face ="bold.italic"), axis.text.y = element_text(face = "bold.italic"))
ggplot(data = Shooting_1, aes(x = Shooting_1$Name, y = Shooting_1$`FG%`, fill = Position), horis=TRUE)+geom_bar(stat = "identity")+labs(title = "Field Goal Percentage Per Game for Spurs Players", x="Names of Players",y="Field Goal Percentage Per Game")+mytheme+coord_flip()
```